Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-02-09 paper/paper.tex
paper: Minor corrections

\section{Related works}
\label{sec:related_works}

@@

For the selection of features, we studied the Melotte 22 dataset. Table~\ref{tab:
sample_features_melotte22_region} describes an example of the region Melotte 22. Each
row represents the features of a star.

\begin{table}[!htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{c|c|c}
        % \textbf{source\_id} &
        \emph{pmra $(mas \cdot yr^{-1})$} & \emph{pmdec $(mas \cdot yr^{-1})$} & \emph{parallax $(mas)$} \\
        \hline
        % 64035217900973056 &
        2.848682 & -3.291204 & 0.399680 \\
        % 64035217900973440 &
        0.894901 & -3.445501 & 0.416639 \\
        % 64035217901215616 &
        7.924372 & -0.241281 & 0.397743 \\
        % 64035351043566208 &
        -4.433802 & -2.584965 & 0.410695 \\
        % 64035385403304960 &
        0.055990 & -1.760018 & 0.413813 \\
      \end{tabular}
    }
    \caption{Features of Melotte 22 region.}
    \label{tab:sample_features_melotte22_region}
  \end{center}
\end{table}

@@

As it was described in Section~\ref{sec:feature_selection}, the number of features we
deal is not too large. This latent space helps us to start in a reduced number of
features and avoids the \emph{"curse of dimensionality"}~\cite{bellman1961curse}.

@@

Figure \ref{fig:kmeans_comparisons_melotte_22} shows an example. It describes the results of
applying K-Means with N=2, N=5 and N=8 in Melotte 22. As we can see, large values of the number
of clusters allow us to isolate more accurately the resonance in parallax at \(\approx 7.3mas\).

@@

Table \ref{tab:results_melotte_25} shows a results summary for Melotte 25.

\begin{table}[!htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{$\mu_{\alpha}$ $(mas \cdot yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas \cdot yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
        \hline
        \textbf{Simbad}\tablefootnote{Results have been taken from the SIMBAD astronomical database\cite{wenger2000simbad}} & 104.92 $\pm$ 0.12 & -28.00 $\pm$ 0.09 & 21.052 $\pm$ 0.065 & - \\
        Clusterix & 106.796 $\pm$ 6.229 & -24.870 $\pm$ 5.417 & 21.210 $\pm$ 1.115 & 109 \\
        K-Means & 79.936 $\pm$ 3.7 & -45.362 $\pm$ 3.8 & 20.901 $\pm$ 0.31 & 374 \\
        DEC & 104.051 $\pm$ 3.2 & -33.424 $\pm$ 2.5 & 22.072 $\pm$ 0.13 & 219 \\
        \textbf{DEC (filt.)} & 105.96 $\pm$ 3.5 & -30.00 $\pm$ 2.4 & 21.74 $\pm$ 0.07 & 175 \\
      \end{tabular}
    }
    \caption{Melotte 25 results.}
    \label{tab:results_melotte_25}
  \end{center}
\end{table}

@@

Figure \ref{fig:result_melotte_25_dec} shows the groups found using the DEC model.
This model labels Melotte 25 as group \emph{g5}.

@@

Table \ref{tab:hyperparameters_melotte_25} shows the hyperparameters
used for the characterization.

\begin{table}[h]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 9 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 11 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{Melotte 25 DEC hyperparameters.}
    \label{tab:hyperparameters_melotte_25}
  \end{center}
\end{table}

@@

\begin{itemize}
  \item NGC 2516 (Ap. \ref{sec:ngc2516}) has it proper motion center deviated from the origin but
        it is embedded inside a big cloud of stars with similar proper motions.
  \item NGC 2632 (Ap. \ref{sec:ngc2632}), in addition to Melotte 22, ia s cluster whose proper motion center
        is not located at the origin and has a well separated parallax center.
  \item NGC 2682 (Ap. \ref{sec:ngc2682}), on the other hand, has its parallax centered within the region's gaussian,
        which complicates its detection although its proper motion center is deviated from the origin.
  \item Melotte 22 (Ap. \ref{sec:melotte22}), as well as Melotte 25, is a cluster closer to us than the other.
        That makes its membership stars to be more scattered than previous clusters which are more compact.
\end{itemize}

All these clusters have a wide variety of diameters, from 25 to 330 arcmin,
as well as the number of stars that belong to them. NGC 2682 has 3,000 stars
while Melotte 25 is located inside a region with more than 400,000 stars.
More information about the studied clusters is available in Table \ref{tab:clusters_summary}.

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{OC} & \emph{$\alpha$ J2000 $(degrees)$} & \emph{$\delta$ J2000 $(degrees)$} & \emph{Radius $(arcmin)$} & \emph{\# stars} \\
        \hline
        NGC 2516 & 119.517 & -60.753 & 15 & 12,869 \\
        NGC 2632 & 130.1 & 19.667 & 35 & 13,167 \\
        NGC 2682 & 132.825 & 11.8 & 12.5 & 2,839 \\
        Melotte 22 & 56.75 & 24.117 & 60 & 61,552 \\
        Melotte 25 & 66.725 & 15.867 & 165 & 433,996 \\
      \end{tabular}
    }
    \caption{Righ ascension, declination, radius and number of stars of studied clusters.
             The number of stars corresponds to those stars contained within a cone of center
             $(\alpha, \delta)$ and raius the cluster's radius multiplied by a factor of 1.5.}
    \label{tab:clusters_summary}
  \end{center}
\end{table}

@@

\subsection{Future works}

@@

\appendix
\section{APPENDIX}
\label{sec:appendix}

@@

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{$\mu_{\alpha}$ $(mas \cdot yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas \cdot yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
        \hline
        \textbf{Simbad} & -4.6579 $\pm$ 0.0075 & 11.1517 $\pm$ 0.0075 & 2.4118 $\pm$ 0.0006 & 1727 \\
        Clusterix & -4.652 $\pm$ 0.523 & 11.203 $\pm$ 0.454 & 2.409 $\pm$ 0.127 & 638 \\
        K-Means & -4.344 $\pm$ 0.14 & 9.507 $\pm$ 0.19 & 2.268 $\pm$ 0.01 & 1542 \\
        DEC & -4.426 $\pm$ 0.17 & 9.952 $\pm$ 0.20 & 2.436 $\pm$ 0.01 & 1532 \\
        \textbf{DEC (filt.)} & -4.502 $\pm$ 0.14 & 10.114 $\pm$ 0.17 & 2.392 $\pm$ 0.004 & 1072 \\
      \end{tabular}
    }
    \caption{NGC 2516 results.}
    \label{tab:app_results_ngc_2516}
  \end{center}
\end{table}

Table \ref{tab:app_results_ngc_2516} shows a results summary for NGC 2516.
The top row of Figure \ref{fig:app_result_ngc_2516_clusterix_kmeans} shows
the characterization using Clusterix+TOPCAT tools while the bottom row
shows eight clusters found by K-Means.

@@

Figure \ref{fig:app_result_ngc_2516_dec} shows the groups found using the
DEC model (top row) and the DEC model filtered (bottom row).
K-Means and DEC have labeled NGC 2516 as \emph{g3}. Although in general,
groups between K-Means and DEC models may not match.
Hyperparameters used in this characterization are listed in Table
\ref{tab:app_hyperparameters_ngc_2516}.

@@

\begin{table}[htbp]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 8 \\
      Clustering Layer & $\left[ 50, 50, 60 \right]$ \\
      Kernel Initializer Seed & 2 \\
      Quantil Threshold & 0.15 \\
    \end{tabular}
    \caption{NGC 2516 DEC hyperparameters.}
    \label{tab:app_hyperparameters_ngc_2516}
  \end{center}
\end{table}

@@

Figure \ref{fig:app_result_ngc_2632_clusterix_kmeans} shows NGC 2632 characterized
by the validation method (first row) and the characterization made by K-Means
showing ten clusters (second row). K-Means labels NGC 2632 as \emph{g1}.

@@

Figure \ref{fig:app_result_ngc_2632_dec} shows the groups found using
the DEC model (first row) and the DEC model filtered (second row).
Open cluster NGC 2632 is labeled as group \emph{g1}.

@@

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{$\mu_{\alpha}$ $(mas \cdot yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas \cdot yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
        \hline
        \textbf{Simbad} & -36.047 $\pm$ 0.110 & -12.917 $\pm$ 0.066 & 5.371 $\pm$ 0.003 & - \\
        Clusterix & -36.154 $\pm$ 1.001 & -12.909 $\pm$ 0.806 & 5.327 $\pm$ 0.187 & 371 \\
        K-Means & -26.352 $\pm$ 0.82 & -15.828 $\pm$ 0.76 & 5.394 $\pm$ 0.03 & 629 \\
        DEC & -20.012 $\pm$ 0.69 & -14.742 $\pm$ 0.58 & 4.686 $\pm$ 0.03 & 894 \\
        \textbf{DEC (filt.)} & -21.571 $\pm$ 0.74 & -14.234 $\pm$ 0.61 & 4.719 $\pm$ 0.03 & 714 \\
      \end{tabular}
    }
    \caption{NGC 2632 results.}
    \label{tab:app_results_ngc_2632}
  \end{center}
\end{table}

Table \ref{tab:app_results_ngc_2632} shows a results summary for NGC 2632 analysis.
While Table \ref{tab:app_hyperparameters_ngc_2632} shows the hyperparameters
used for characterizing NGC 2632 with our model.

\begin{table}[htbp]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 10 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 10 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2632 DEC hyperparameters.}
    \label{tab:app_hyperparameters_ngc_2632}
  \end{center}
\end{table}

@@

Table \ref{tab:app_results_ngc_2682} shows a results summary for NGC 2682.

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{$\mu_{\alpha}$ $(mas \cdot yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas \cdot yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
        \hline
        \textbf{Simbad} & -10.9737 $\pm$ 0.0064 & -2.9396 $\pm$ 0.0063 & 1.1325 $\pm$ 0.0011 & 1194 \\
        Clusterix+TOPCAT & -10.970 $\pm$ 0.322 & -2.958 $\pm$ 0.327 & 1.142 $\pm$ 0.080 & 649 \\
        K-Means & -8.616 $\pm$ 0.15 & -3.710 $\pm$ 0.16 & 1.196 $\pm$ 0.01 & 1374 \\
        DEC & -8.926 $\pm$ 0.15 & -3.550 $\pm$ 0.15 & 1.144 $\pm$ 0.005 & 1238 \\
        \textbf{DEC (filt.)} & -9.619 $\pm$ 0.13 & -3.317 $\pm$ 0.13 & 1.140 $\pm$ 0.003 & 990 \\
      \end{tabular}
    }
    \caption{NGC 2682 results.}
    \label{tab:app_results_ngc_2682}
  \end{center}
\end{table}

Figure \ref{fig:app_result_ngc_2682_clusterix_kmeans} shows
NGC 2682 characterized using Clusterix+TOPCAT tools (top row)
and ten clusters identified by K-Means (bottom row).
The chacterization made by K-Means labels NGC 2682 as group \emph{g4}.

@@

Figure \ref{fig:app_result_ngc_2682_dec} shows the groups found using
the DEC model (first row) and the DEC model filtered (second row).
The cluster of interest is the group \emph{g2}.

@@

Table \ref{tab:app_hyperparameters_ngc_2682} shows the
hyperparameters used for characterizing NGC 2682 with DEC method.

\begin{table}[htbp]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 10 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 0 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2682 DEC hyperparameters.}
    \label{tab:app_hyperparameters_ngc_2682}
  \end{center}
\end{table}

\subsection{MELOTTE 22}
\label{sec:melotte22}

@@

Figure \ref{fig:app_result_melotte_22_clusterix_kmeans} shows Melotte 22
characterized using Clusterix+TOPCAT tools (top row) and the characterization
made by K-Means (bottom row) showing nine clusters. Melotte 22 is labeled as
group \emph{g1}.

Figure \ref{fig:app_result_melotte_22_dec} shows the groups found using
DEC model (first row) and DEC model filtered (second row).
Melotte 22 is labeled as group \emph{g2} by DEC model.

@@

Table \ref{tab:app_results_melotte_22} shows a results summary for Melotte 22.

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{$\mu_{\alpha}$ $(mas \cdot yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas \cdot yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
        \hline
        \textbf{Simbad} & 19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
        Clusterix & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
        K-Means & 20.25 $\pm$ 0.95 & -38.01 $\pm$ 1.08 & 7.23 $\pm$ 0.06 & 1378 \\
        DEC & 23.67 $\pm$ 1.29 & -46.23 $\pm$ 1.50 & 8.04 $\pm$ 0.09 & 878 \\
        \textbf{DEC (filt.)} & 19.50 $\pm$ 0.41 & -44.23 $\pm$ 0.39 & 7.42 $\pm$ 0.005 & 438 \\
      \end{tabular}
    }
    \caption{Melotte 22 results.}
    \label{tab:app_results_melotte_22}
  \end{center}
\end{table}

While Table \ref{tab:app_hyperparameters_melotte_22} shows the hyperparameters
used for characterizing Melotte 22 with the DEC model.

\begin{table}[hbtp]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 5 \\
      Clustering Layer & $\left[ 50, 50, 200 \right]$ \\
      Kernel Initializer Seed & 11 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{Melotte 22 DEC hyperparameters.}
    \label{tab:app_hyperparameters_melotte_22}
  \end{center}
\end{table}

\renewcommand{\refname}{REFERENCES}
\bibliographystyle{unsrt}
\bibliography{references}

>>>>

\section{Related work}
\label{sec:related_works}

@@

For the selection of features, we studied the Melotte 22 dataset.
Table~\ref{tab:sample_features_melotte22_region} describes an example of the region Melotte 22.
Each row represents the features of a star.

\begin{table}[!htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{c|c|c}
        % \textbf{source\_id} &
        \emph{pmra \((mas \cdot yr^{-1})\)} & \emph{pmdec \((mas \cdot yr^{-1})\)} & \emph{parallax \((mas)\)} \\
        \hline
        % 64035217900973056 &
        2.848682 & -3.291204 & 0.399680 \\
        % 64035217900973440 &
        0.894901 & -3.445501 & 0.416639 \\
        % 64035217901215616 &
        7.924372 & -0.241281 & 0.397743 \\
        % 64035351043566208 &
        -4.433802 & -2.584965 & 0.410695 \\
        % 64035385403304960 &
        0.055990 & -1.760018 & 0.413813 \\
      \end{tabular}
    }
    \caption{Features of Melotte 22 region.}
    \label{tab:sample_features_melotte22_region}
  \end{center}
\end{table}

@@

As it was described in Section~\ref{sec:feature_selection}, the number of features we
deal is not too large. This latent space helps us to start in a reduced number of
features and avoids the \emph{``curse of dimensionality``}~\cite{bellman1961curse}.

@@

Figure~\ref{fig:kmeans_comparisons_melotte_22} shows an example. It describes the results of
applying K-Means with N=2, N=5 and N=8 in Melotte 22. As we can see, large values of the number
of clusters allow us to isolate more accurately the resonance in parallax at \(\approx 7.3mas\).

@@

Table~\ref{tab:results_melotte_25} shows a results summary for Melotte 25.

\begin{table}[!htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{\(\mu_{\alpha}\) \((mas \cdot yr^{-1})\)} & \emph{\(\mu_{\delta}\) \((mas \cdot yr^{-1})\)}
        & \emph{\( \varpi \) \((mas)\)} & \emph{\# stars} \\
        \hline
        \textbf{Simbad}\tablefootnote{Results have been taken from the SIMBAD astronomical database\cite{wenger2000simbad}}
        & 104.92 \( \pm \) 0.12 & -28.00 \( \pm \) 0.09 & 21.052 \( \pm \) 0.065 & - \\
        Clusterix & 106.796 \( \pm \) 6.229 & -24.870 \( \pm \) 5.417 & 21.210 \( \pm \) 1.115 & 109 \\
        K-Means & 79.936 \( \pm \) 3.7 & -45.362 \( \pm \) 3.8 & 20.901 \( \pm \) 0.31 & 374 \\
        DEC & 104.051 \( \pm \) 3.2 & -33.424 \( \pm \) 2.5 & 22.072 \( \pm \) 0.13 & 219 \\
        \textbf{DEC (filt.)} & 105.96 \( \pm \) 3.5 & -30.00 \( \pm \) 2.4 & 21.74 \( \pm \) 0.07 & 175 \\
      \end{tabular}
    }
    \caption{Melotte 25 results.}
    \label{tab:results_melotte_25}
  \end{center}
\end{table}

@@

Figure~\ref{fig:result_melotte_25_dec} shows the groups found using the DEC model.
This model labels Melotte 25 as group \emph{g5}.

@@

Table~\ref{tab:hyperparameters_melotte_25} shows the hyperparameters
used for the characterization.

\begin{table}[h]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 9 \\
      Clustering Layer & \(\left[ 50, 50, 40 \right]\) \\
      Kernel Initializer Seed & 11 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{Melotte 25 DEC hyperparameters.}
    \label{tab:hyperparameters_melotte_25}
  \end{center}
\end{table}

@@

\begin{itemize}
  \item NGC 2516 (Ap.~\ref{sec:ngc2516}) has it proper motion center deviated from the origin but
        it is embedded inside a big cloud of stars with similar proper motions.
  \item NGC 2632 (Ap.~\ref{sec:ngc2632}), in addition to Melotte 22, ia s cluster whose proper motion center
        is not located at the origin and has a well separated parallax center.
  \item NGC 2682 (Ap.~\ref{sec:ngc2682}), on the other hand, has its parallax centered within the region's gaussian,
        which complicates its detection although its proper motion center is deviated from the origin.
  \item Melotte 22 (Ap.~\ref{sec:melotte22}), as well as Melotte 25, is a cluster closer to us than the other.
        That makes its membership stars to be more scattered than previous clusters which are more compact.
\end{itemize}

All these clusters have a wide variety of diameters, from 25 to 330 arcmin,
as well as the number of stars that belong to them. NGC 2682 has 3,000 stars
while Melotte 25 is located inside a region with more than 400,000 stars.
More information about the studied clusters is available in Table~\ref{tab:clusters_summary}.

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{OC} & \emph{\( \alpha \) J2000 \((degrees)\)} & \emph{\( \delta \) J2000 \((degrees)\)}
        & \emph{Radius \((arcmin)\)} & \emph{\# stars} \\
        \hline
        NGC 2516 & 119.517 & -60.753 & 15 & 12,869 \\
        NGC 2632 & 130.1 & 19.667 & 35 & 13,167 \\
        NGC 2682 & 132.825 & 11.8 & 12.5 & 2,839 \\
        Melotte 22 & 56.75 & 24.117 & 60 & 61,552 \\
        Melotte 25 & 66.725 & 15.867 & 165 & 433,996 \\
      \end{tabular}
    }
    \caption{Right ascension, declination, radius and number of stars of studied clusters.
             The number of stars corresponds to those stars contained within a cone of center
             \((\alpha, \delta)\) and radius the cluster's radius multiplied by a factor of 1.5.}
    \label{tab:clusters_summary}
  \end{center}
\end{table}

@@

\subsection{Future work}

@@

\appendix
\section{Appendix}
\label{sec:appendix}

@@

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{\(\mu_{\alpha}\) \((mas \cdot yr^{-1})\)} & \emph{\(\mu_{\delta}\) \((mas \cdot yr^{-1})\)}
        & \emph{\( \varpi \) \((mas)\)} & \emph{\# stars} \\
        \hline
        \textbf{Simbad} & -4.6579 \( \pm \) 0.0075 & 11.1517 \( \pm \) 0.0075 & 2.4118 \( \pm \) 0.0006 & 1727 \\
        Clusterix & -4.652 \( \pm \) 0.523 & 11.203 \( \pm \) 0.454 & 2.409 \( \pm \) 0.127 & 638 \\
        K-Means & -4.344 \( \pm \) 0.14 & 9.507 \( \pm \) 0.19 & 2.268 \( \pm \) 0.01 & 1542 \\
        DEC & -4.426 \( \pm \) 0.17 & 9.952 \( \pm \) 0.20 & 2.436 \( \pm \) 0.01 & 1532 \\
        \textbf{DEC (filt.)} & -4.502 \( \pm \) 0.14 & 10.114 \( \pm \) 0.17 & 2.392 \( \pm \) 0.004 & 1072 \\
      \end{tabular}
    }
    \caption{NGC 2516 results.}
    \label{tab:app_results_ngc_2516}
  \end{center}
\end{table}

Table~\ref{tab:app_results_ngc_2516} shows a results summary for NGC 2516.
The top row of Figure~\ref{fig:app_result_ngc_2516_clusterix_kmeans} shows
the characterization using Clusterix+TOPCAT tools while the bottom row
shows eight clusters found by K-Means.

@@

Figure~\ref{fig:app_result_ngc_2516_dec} shows the groups found using the
DEC model (top row) and the DEC model filtered (bottom row).
K-Means and DEC have labeled NGC 2516 as \emph{g3}. Although in general,
groups between K-Means and DEC models may not match.
Hyperparameters used in this characterization are listed in
Table~\ref{tab:app_hyperparameters_ngc_2516}.

@@

\begin{table}[htbp]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 8 \\
      Clustering Layer & \(\left[ 50, 50, 60 \right]\) \\
      Kernel Initializer Seed & 2 \\
      Quantil Threshold & 0.15 \\
    \end{tabular}
    \caption{NGC 2516 DEC hyperparameters.}
    \label{tab:app_hyperparameters_ngc_2516}
  \end{center}
\end{table}

@@

Figure~\ref{fig:app_result_ngc_2632_clusterix_kmeans} shows NGC 2632 characterized
by the validation method (first row) and the characterization made by K-Means
showing ten clusters (second row). K-Means labels NGC 2632 as \emph{g1}.

@@

Figure~\ref{fig:app_result_ngc_2632_dec} shows the groups found using
the DEC model (first row) and the DEC model filtered (second row).
Open cluster NGC 2632 is labeled as group \emph{g1}.

@@

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{\(\mu_{\alpha}\) \((mas \cdot yr^{-1})\)} & \emph{\(\mu_{\delta}\) \((mas \cdot yr^{-1})\)}
        & \emph{\( \varpi \) \((mas)\)} & \emph{\# stars} \\
        \hline
        \textbf{Simbad} & -36.047 \( \pm \) 0.110 & -12.917 \( \pm \) 0.066 & 5.371 \( \pm \) 0.003 & - \\
        Clusterix & -36.154 \( \pm \) 1.001 & -12.909 \( \pm \) 0.806 & 5.327 \( \pm \) 0.187 & 371 \\
        K-Means & -26.352 \( \pm \) 0.82 & -15.828 \( \pm \) 0.76 & 5.394 \( \pm \) 0.03 & 629 \\
        DEC & -20.012 \( \pm \) 0.69 & -14.742 \( \pm \) 0.58 & 4.686 \( \pm \) 0.03 & 894 \\
        \textbf{DEC (filt.)} & -21.571 \( \pm \) 0.74 & -14.234 \( \pm \) 0.61 & 4.719 \( \pm \) 0.03 & 714 \\
      \end{tabular}
    }
    \caption{NGC 2632 results.}
    \label{tab:app_results_ngc_2632}
  \end{center}
\end{table}

Table~\ref{tab:app_results_ngc_2632} shows a results summary for NGC 2632 analysis.
While Table~\ref{tab:app_hyperparameters_ngc_2632} shows the hyperparameters
used for characterizing NGC 2632 with our model.

\begin{table}[htbp]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 10 \\
      Clustering Layer & \(\left[ 50, 50, 40 \right]\) \\
      Kernel Initializer Seed & 10 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2632 DEC hyperparameters.}
    \label{tab:app_hyperparameters_ngc_2632}
  \end{center}
\end{table}

@@

Table~\ref{tab:app_results_ngc_2682} shows a results summary for NGC 2682.

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{\(\mu_{\alpha}\) \((mas \cdot yr^{-1})\)} & \emph{\(\mu_{\delta}\) \((mas \cdot yr^{-1})\)}
        & \emph{\( \varpi \) \((mas)\)} & \emph{\# stars} \\
        \hline
        \textbf{Simbad} & -10.9737 \( \pm \) 0.0064 & -2.9396 \( \pm \) 0.0063 & 1.1325 \( \pm \) 0.0011 & 1194 \\
        Clusterix+TOPCAT & -10.970 \( \pm \) 0.322 & -2.958 \( \pm \) 0.327 & 1.142 \( \pm \) 0.080 & 649 \\
        K-Means & -8.616 \( \pm \) 0.15 & -3.710 \( \pm \) 0.16 & 1.196 \( \pm \) 0.01 & 1374 \\
        DEC & -8.926 \( \pm \) 0.15 & -3.550 \( \pm \) 0.15 & 1.144 \( \pm \) 0.005 & 1238 \\
        \textbf{DEC (filt.)} & -9.619 \( \pm \) 0.13 & -3.317 \( \pm \) 0.13 & 1.140 \( \pm \) 0.003 & 990 \\
      \end{tabular}
    }
    \caption{NGC 2682 results.}
    \label{tab:app_results_ngc_2682}
  \end{center}
\end{table}

Figure~\ref{fig:app_result_ngc_2682_clusterix_kmeans} shows
NGC 2682 characterized using Clusterix+TOPCAT tools (top row)
and ten clusters identified by K-Means (bottom row).
The characterization made by K-Means labels NGC 2682 as group \emph{g4}.

@@

Figure~\ref{fig:app_result_ngc_2682_dec} shows the groups found using
the DEC model (first row) and the DEC model filtered (second row).
The cluster of interest is the group \emph{g2}.

@@

Table~\ref{tab:app_hyperparameters_ngc_2682} shows the
hyperparameters used for characterizing NGC 2682 with DEC method.

\begin{table}[htbp]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 10 \\
      Clustering Layer & \(\left[ 50, 50, 40 \right]\) \\
      Kernel Initializer Seed & 0 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2682 DEC hyperparameters.}
    \label{tab:app_hyperparameters_ngc_2682}
  \end{center}
\end{table}

\subsection{Melotte 22}
\label{sec:melotte22}

@@

Figure~\ref{fig:app_result_melotte_22_clusterix_kmeans} shows Melotte 22
characterized using Clusterix+TOPCAT tools (top row) and the characterization
made by K-Means (bottom row) showing nine clusters. Melotte 22 is labeled as
group \emph{g1}.

Figure~\ref{fig:app_result_melotte_22_dec} shows the groups found using
DEC model (first row) and DEC model filtered (second row).
Melotte 22 is labeled as group \emph{g2} by DEC model.

@@

Table~\ref{tab:app_results_melotte_22} shows a results summary for Melotte 22.

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{\(\mu_{\alpha}\) \((mas \cdot yr^{-1})\)} & \emph{\(\mu_{\delta}\) \((mas \cdot yr^{-1})\)}
        & \emph{\( \varpi \) \((mas)\)} & \emph{\# stars} \\
        \hline
        \textbf{Simbad} & 19.997 \( \pm \) 0.127 & -45.548 \( \pm \) 0.101 & 7.364 \( \pm \) 0.005 & 1326 \\
        Clusterix & 19.98 \( \pm \) 1.25 & -45.47 \( \pm \) 1.48 & 7.33 \( \pm \) 0.21 & 634 \\
        K-Means & 20.25 \( \pm \) 0.95 & -38.01 \( \pm \) 1.08 & 7.23 \( \pm \) 0.06 & 1378 \\
        DEC & 23.67 \( \pm \) 1.29 & -46.23 \( \pm \) 1.50 & 8.04 \( \pm \) 0.09 & 878 \\
        \textbf{DEC (filt.)} & 19.50 \( \pm \) 0.41 & -44.23 \( \pm \) 0.39 & 7.42 \( \pm \) 0.005 & 438 \\
      \end{tabular}
    }
    \caption{Melotte 22 results.}
    \label{tab:app_results_melotte_22}
  \end{center}
\end{table}

While Table~\ref{tab:app_hyperparameters_melotte_22} shows the hyperparameters
used for characterizing Melotte 22 with the DEC model.

\begin{table}[hbtp]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 5 \\
      Clustering Layer & \(\left[ 50, 50, 200 \right]\) \\
      Kernel Initializer Seed & 11 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{Melotte 22 DEC hyperparameters.}
    \label{tab:app_hyperparameters_melotte_22}
  \end{center}
\end{table}

\renewcommand{\refname}{References}
\bibliographystyle{unsrt}
\bibliography{references}
